%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Plain Cover Letter
% LaTeX Template
% Version 1.0 (28/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute 
% http://www.rpi.edu/dept/arc/training/latex/resumes/
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt,a4paper,sans]{letter} % Default font size of the document, change to 10pt to fit more text

\usepackage{newcent} % Default font is the New Century Schoolbook PostScript font 
%\usepackage{helvet} % Uncomment this (while commenting the above line) to use the Helvetica font

% Margins
\topmargin=-1in % Moves the top of the document 1 inch above the default
\textheight=8.5in % Total height of the text on the page before text goes on to the next page, this can be increased in a longer letter
\oddsidemargin=-10pt % Position of the left margin, can be negative or positive if you want more or less room
\textwidth=6.5in % Total width of the text, increase this if the left margin was decreased and vice-versa
\date{}
\let\raggedleft\raggedright % Pushes the date (at the top) to the left, comment this line to have the date on the right

\begin{document}

%----------------------------------------------------------------------------------------
%	ADDRESSEE SECTION
%----------------------------------------------------------------------------------------

%\begin{letter}{}





%----------------------------------------------------------------------------------------
%	YOUR NAME & ADDRESS SECTION
%----------------------------------------------------------------------------------------

%\begin{center}
%\large\bf Dr. John Smith \\ % Your name
%%\vspace{20pt} \hrule height 1pt % If you would like a horizontal line separating the name from the address, uncomment the line to the left of this text
%123 Broadway \\ City, State 12345 \\ (000) 111-1111 % Your address and phone number
%\end{center} 
%\vfill

%\signature{John Smith} % Your name for the signature at the bottom

%----------------------------------------------------------------------------------------
%	LETTER CONTENT SECTION
%----------------------------------------------------------------------------------------

%\opening{Dear Prof. Chua and Chen,} 
 
I am writing to express my sincere interest in Caltech's postdoctoral research position at TAPIR. I would love to
    pursure my postdoctoral studies as a member of your team. I am a postdoctoral fellow of Sun Yat-sen university where
    I research the black holes by gravitational waves.

In my research, I focus on studying stellar- and intermediate-mass black holes by gravitational wave detectors, such
    as LISA and TianQin. In my doctoral studies, I worked to explore stellar-mass
    binary black holes by TianQin, as well as the joint observation with LISA,. In the post doctoral stage, I shift my
    attention to intermediate-mass black holes. I studied the detection capacity of TianQin and LISA for
    GW190521-like binary black holes whose merger remnants are intermediate-mass black holes. Currently, I have been
    working on studying the intermediate-mass black holes in globular clusters by gravitation wave detection for the
    hierachical triple systems. In the future, I am going to explore the intermediate-mass binary black holes formed by
    population III stars by gravitational waves.

I would appreciate the opportunity to continue my research in your team. I
    believe that the nature of my research is extremely relevant to your efforts. I think my knowledge and
    experience surrounding detection for stellar- and intermediate-mass black holes could aid in your research.

I am a self-motivated, independent researcher with passionate for science. I feel my research on stellar- and
    intermediate-mass black holes, grant proposal writing could be a major asset to your team, as a detail-oriented,
    qualified and creative dandidate. I have attached my CV and would be very interested in setting up a time further
    discuss my skills and qualifications with you. Please let me know whether you have quesitons and I look forward to
    hearing from you.\\


Sincerely,

Shuai Liu


%\encl{Curriculum vitae, employment form} % List your enclosed documents here, comment this out to get rid of the "encl:"

%----------------------------------------------------------------------------------------

%\end{letter}

\end{document}
