%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Plain Cover Letter
% LaTeX Template
% Version 1.0 (28/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute 
% http://www.rpi.edu/dept/arc/training/latex/resumes/
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt,a4paper,sans]{letter} % Default font size of the document, change to 10pt to fit more text

%\usepackage{newcent} % Default font is the New Century Schoolbook PostScript font 
%\usepackage{helvet} % Uncomment this (while commenting the above line) to use the Helvetica font

% Margins
\topmargin=-1in % Moves the top of the document 1 inch above the default
\textheight=9in%8.5in % Total height of the text on the page before text goes on to the next page, this can be increased in a longer letter
\oddsidemargin=-10pt % Position of the left margin, can be negative or positive if you want more or less room
\textwidth=6.5in % Total width of the text, increase this if the left margin was decreased and vice-versa
\date{}
\let\raggedleft\raggedright % Pushes the date (at the top) to the left, comment this line to have the date on the right

\begin{document}

%----------------------------------------------------------------------------------------
%	ADDRESSEE SECTION
%----------------------------------------------------------------------------------------

\begin{letter}{March 20 2022 \\
Prof. Alvin Chua and Prof. Yanbei Chen \\
California Institute of Technology \\
1200 E California Blvd \\ 
Pasadena, CA 91125, United States}

Shuai Liu \\
TianQin Research Center for Gravitational Physics \\
Zhuhai Campus Sun Yat-sen University \\
Tangjiawan, Zhuhai 519082 \\
Guangdong, People's Republic of China \\
shuai.liu.1990@outlook.com




%----------------------------------------------------------------------------------------
%	YOUR NAME & ADDRESS SECTION
%----------------------------------------------------------------------------------------

%\begin{center}
%\large\bf Dr. John Smith \\ % Your name
%%\vspace{20pt} \hrule height 1pt % If you would like a horizontal line separating the name from the address, uncomment the line to the left of this text
%123 Broadway \\ City, State 12345 \\ (000) 111-1111 % Your address and phone number
%\end{center} 
%\vfill

%\signature{John Smith} % Your name for the signature at the bottom

%----------------------------------------------------------------------------------------
%	LETTER CONTENT SECTION
%----------------------------------------------------------------------------------------

\opening{To whom it may concern,} 
 
I am writing to express my sincere interest in the Caltech's postdoctoral research position at TAPIR. I would love to
pursue my postdoctoral studies as a member of your team. I am a postdoctoral fellow of Sun Yat-sen University where
I study the black holes by gravitational waves.

In my research, I focus on studying stellar- and intermediate-mass black holes by gravitational wave detectors, such
as LISA and TianQin. In the stage as a doctoral candidate, I worked to explore stellar-mass
binary black holes by TianQin, as well as the joint observation with LISA. In the postdoctoral stage, I shift my
attention to intermediate-mass black holes. I studied the detection capacity of TianQin and LISA for
GW190521-like binary black holes whose merger remnants are intermediate-mass black holes. Currently, I have been
working on studying the intermediate-mass black holes in globular clusters by gravitation wave detection for the
hierarchical triple systems. In the future, I am going to explore the intermediate-mass binary black holes formed by
population III stars by gravitational waves. My current and future researches are relative to position which focuses on extreme-mass-ratio binary inspirals, because they also involve the systems consisting of objects
with large mass ratios, the modeling of sources, and the dynamic
interactions in dense environments. In addition, my future research will contribute to the
scientific payoff of LISA, because IMBBH is also an important class gravitational wave
source for it.

I would appreciate the opportunity to continue my research in your team. I
believe that the nature of my research is relevant to your efforts. I think my knowledge and
experience surrounding detection for stellar- and intermediate-mass black holes could aid in your research.

I am a self-motivated, independent researcher with the passion for science. I feel my research on stellar- and
intermediate-mass black holes, grant proposal writing could be a major asset to your team, as a detail-oriented,
qualified, and creative candidate. I have attached my CV and would be very interested in setting up a time further
discuss my skills and qualifications with you. Please let me know whether you have questions and I look forward to
hearing from you.\\


Sincerely,

Shuai Liu


%\encl{Curriculum vitae, employment form} % List your enclosed documents here, comment this out to get rid of the "encl:"

%----------------------------------------------------------------------------------------

\end{letter}

\end{document}
