%!TEX encoding = UTF8
%!TEX root =cv-llt.tex

\begin{rubric}{Conferences and Invited Talks}
    \entry*[2023] \textbf{Invited talk at Kavli Institute for Astronomy and Astrophysics, Peking University, Beijing,} Exploring Stellar- and Intermediate-mass Black Holes with Space-borne Gravitational Wave Detectors.
    \entry*[2022] \textbf{The 2022 annual meeting of Division of Gravitation and Relativistic Astrophysics, Chinese Physical Society,} Studying stellar mass binary black holes with space-borne gravitational wave detectors.
    \entry*[2022] \textbf{Invited talk at Gravitational wave next conference on Zoom,} Studying stellar mass
    binary black holes with space-borne gravitational wave detectors.
    \entry*[2022] \textbf{Invited talk at Southern University of Science and Technology, Shenzhen,} Detecting stellar mass
    binary black holes with TianQin. 
    \entry*[2021] \textbf{Youth Symposium of Chongqing University and University of Science and Technology of China,
    Chongqing,} Science with TianQin observatory: Preliminary results on stellar mass binary black holes.
    \entry*[2021] \textbf{The Gravitational-wave Excellence through Alliance Training (GrEAT) Network with China on
    Zoom,} Science with TianQin observatory: Preliminary results on stellar mass binary black holes.
    \entry*[2020] \textbf{The 13th Beijing Guangzhou Xiamen astrophysics Symposium, Xiamen,} Science with
    TianQin observatory: Preliminary results on stellar mass binary black holes.
    \entry*[2020] \textbf{The 7th KAGRA International Workshop on Zoom,} Science with
    TianQin observatory: Preliminary results on stellar mass binary black holes.
    \entry*[2019] \textbf{The annual symposium of TianQin center of Sun Yet-sen University and gravitational center of
    Huazhong University of Science and Technology,
    Wuhan,} The study for detecting stellar mass binary black holes with TianQin. 
    \entry*[2018] \textbf{The annual symposium of TianQin center of Sun Yet-sen University and gravitational center of
    Huazhong University of Science and Technology,
    Wuhan,} The study for detecting stellar mass binary black holes with TianQin, poster.
\end{rubric}
